\subsection{Paradigmatic vs Syntagmatic Representations of Word Context}
\label{sec:pvss}

To get a direct comparison of the paradigmatic and syntagmatic context
representations we feed 4 different co-occurrences defined in
Section~\ref{sec:representation} into the S-CODE algorithm.  The first
model accepts word ($W$) - right bigram ($C$) pairs as the input, the
second model accepts word ($W$) - left bigram($C$) pairs as the input,
the third model accepts word ($W$) - concatenation of the left and
right bigrams ($C$) pairs \cite{mintz2003frequent} as the input and
the final model accepts words ($W$) - left bigram($C_1$) and right
bigram ($C_2$) tuples \cite{20674613} as the input to the S-CODE.
Finally, we cluster the word type embeddings ($W$) with k-means
algorithm and report the results on Table \ref{tab:syntagmatic}.
\begin{table*}[ht]
\centering
\caption{Summary of results in terms of the \mto\ and \vm\ scores of
  the S-CODE algorithm when the paradigmatic or syntagmatic
  representations are feed as an input.  Standard errors are given in
  parentheses when available.  Results of the statistically best
  performing system are written in bold.  We do not report the
  original results of Maron et al. \protect\shortcite{maron2010sphere}
  since our replication achieves higher accuracies.}
\begin{tabular}{|l|l|l|}
\hline
Input & \mto & \vm\\
\hline
$W$ (word) - $C$ (right bigram) & .6625 (.0115) & .5809 (.0066)\\
$W$ (word) - $C$ (left bigram) & .6604 (.0054) & .5983 (.0028)\\
$W$ (word) - $C$ (left and right bigram concatenation) & .7268 (.0091) & .6416 (.0052)\\
$W$ (word) - $C_1$, $C_2$ (left and right bigrams) & .7173 (.0061) & .6381 (.0032)\\
Maron et al. \shortcite{maron2010sphere}(replication)  & \bgmto & \bgvm \\
$W$ (word) - $C$ (random substitutes) & {\bf\wsmto} & {\bf\wsvm} \\
\hline
\end{tabular}
\label{tab:syntagmatic}
\end{table*}

To replicate the work of Maron et al. \shortcite{maron2010sphere} we
feed word ($W$) - right bigram ($C$) pairs as the input.  At the end
each word $w$ in the vocabulary ends up with two points on the sphere,
a $\phi_w$ point representing the behavior of $w$ as the left word of
a bigram and a $\psi_w$ point representing it as the right word.  The
two vectors for $w$ are concatenated to create a 50-dimensional
representation at the end.  These 50-dimensional vectors are clustered
using the k-means algorithm.  Maron et al. \shortcite{maron2010sphere}
report many-to-one scores of .6880 (.0016) for 45 clusters and .7150
(.0060) for 50 clusters (on the PTB).  Using our default settings the
bigram model achieves \bgmto\ \mto\ and \bgvm\ \vm\ accuracies.  Table
\ref{tab:syntagmatic} summarizes all the results and shows that the
paradigmatic representation accuracies are significantly higher than
the syntagmatic representation \mto\ and \vm\ accuracies.
